---
title: "Statewise Covid-19 Population"
output: html_document
---
Tracy Tai, Olachi Mbara, Luong Tran Thanh Quan

### Introduction

As Covid-19 spreads through the world, many people have suffered in 
this pandemic. As a result, people have changed their life style 
dramatically to stay healthy, including work from home, online teaching 
courses, and so on. Economics have also encountered tremendous 
challenges. Restaurants, shopping malls and gyms are all closed to keep 
Covid-19 from spreading, and resulted in companies facing great loss. In
this project, we want to use data visualization to show how Covid-19 
effect individuals and economy in each state, and compare data from each
state.
  
```{r setup, include=FALSE}
library("knitr")
knitr::opts_chunk$set(echo = TRUE)

source("chart1.R")
source("summary.R")
source("chart2.R")
source("chart3.R")
source("table.R")
options(scipen=999)

```

```{r, include=FALSE}
#summary info
state_highest_cases <-summary_info$state_highest_cases
num_highest_state <- summary_info$num_highest_state
num_lowest_state <- summary_info$num_lowest_state
state_lowest_infections <- summary_info$state_lowest_infections
top_10 <- summary_info$top_10
```
### Summary

In our analysis, `r state_highest_cases` has the most Covid-19 infected 
cases among other states, with `r num_highest_state` Covid-19 cases. It 
in our commonsense that state with high civil population are more likely
to have a high Covid-19 infected population, and our data and graph also
supports this conclusion. The lowest Covid-19 cases is `r num_lowest_state` in 
`r state_lowest_infections`. In our data set, the ten states with most 
Covid-19 cases are `r top_10`. Therefore, the number of Covid-19 
infected people is related to the civil population of a state. Under 
Covid-19, we should all follow safety instructions and stay healthy for 
the sake of ourselves and our families, especially when you are living 
in a state with large Covid-19 cases. 


### Aggregated Table

```{r, echo=FALSE, message=FALSE}
kable(combine_df)

```
      
In this table, we concluded several infomation we used to compute our
analysis. We ranked the states by its state GDP, and then added
population and density column to see how we can generate useful
information from these values. This table can be compared with our first
graph, to see if there's a relationship between these values and 
Covid-19 cases. Some insights from this table would be the relationship 
found between state GDP, state density and population. As population 
increases, state GDP are likely to increase as well.The top five states 
with highest stateGDP also have a high population. On the other hand, 
state density did not relate to stateGDP as we predicted. 


```{r, echo=FALSE, message=FALSE}
plot(infected_bar_chart)
```
  
The purpose of creating this figure was to compare the results with the 
table graph to find relationships between stateGDP, population and 
Covid-19 cases. This chart presented the ten states with most Covid-19 
infected cases. We can see from this chart that the top three states are
California, Texas and Florida. These three states has cases over 800,000
cases, and the following states are all under 500,000 cases. This
discrepancy also corresponds to the top three states in the table graph,
with Florida being switched to New York. This bar chart and table chart 
nicely showed the relationship between Covid-19 cases and population: 
states with higher civil population are likely to have a higher Covid-19
infected population. 


```{r, echo=FALSE}
plot(pie_chart_theme)

```

This pie chart was created to show how the top five states in state GDP
distribute in proportion. Pie chart is best at representing proportion
and comparisons between states. We want to use the most straigntforward
method to visualize data and make our data easy to read and understand.
From this chart we can see that the top two states filled more than half
of the whole pie chart, meaning that the top states has much higher
state GDP, and there is a huge discrepancy between the states. This
situation raised a question that what Covid-19 related factor in state
economics have caused this discrepancy.

```{r, echo=FALSE}
plot(chart3)

```
    
This chart was intended to show how Covid-19 infected population spreads
throughout the country. This map presented the distribution of Covid-19
infected population, and be aware of the states with high infected
populations. As we can see from this map, we could conclude that
California and Texas are states with large Covid-19 infected population.
We should all stay safe and protect ourselves in this situation. 


